---
title: "Penguin_Practice_No1"
author: Mila 
output: html_document
date: "2022-09-08"
---


Here are some practice problems to explore the penguins dataset. First we need to load the penguin dataset

```{r}
library("palmerpenguins")
```


If you can't remember how to do something, look back at Intro to R.Rmd.

1. What is the mean and standard deviation of bill length of the penguins?
```{r}
# create a variable that contains only the column for bill depth

# mean 

# standard deviation

```


2. What is the mean and standard deviation of the body mass of the penguins?
```{r}
# create a variable that contains only the column for body mass

# mean

# standard deviation


```


3. What is the mean and median flipper length of the penguins? 
```{r}
# create a variable that contains only the column for flipper length

# mean

# median

```

4. How long are the largest flippers in this dataset? How long is the shortest? (Hint: google how to find the minimum and maximum values in a vector). You can use the same variable that you created in 3!
```{r}
# longest flipper length

# shortest flipper length

```


5. What is the range of bill depths of penguins? (Range is the maximum value - minimum value)
```{r}
# deepest bill depth

# shallowest bill depth

# range of bill depth
```

6. How many species of penguins are in this dataset? List them using comments. 
```{r}

```

7. Find the value for the longest bill in the dataset. Assign it to the variable longestBill. 
```{r}

```

8. Calculate the variance of body mass. (Hint: google variance in R)
```{r}

```

9. Calculate the variance of flipper length.
```{r}

```

10. Calculate and compare the standard deviation of bill length and bill depth. Which has a larger standard deviation?
```{r}
# standard deviation of bill length

# standard deviation of bill depth

# Which has a larger standard deviation? 
```

