---
title: "Intro - Problem Set"
output: pdf_document
---

# Problem Set for Intro to R

### Your Name (replace me)

### Date (replace me)

**DUE THURSDAY, Sept 8th AT MIDNIGHT**\
Download this file, and turn it in on Moodle.\
\
(to download a file, check the checkbox next to the file in the lower-right window, and click the gear, then Export....)

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

1.  In the code chunk below, define what a variable is (using comments), and create a variable `myVariable` set equal to 20.

```{r}



```

2.  Describe what a vector is in R, and create a sample vector below:

```{r}




```

3.  In the code chunk below, load the tidyverse. Why might we do this, and what is the tidyverse for?

```{r}


```

4.  Describe what a function is. What is an argument? How might you learn about what functions exist in R?

```{r}



```

5.  What is camel case? Describe some best practices for naming variables.

```{r}




```

6.  What is the mean for the survey responses for self reported willingness to settle in a remote environment (hint: use the `remote` column)

```{r}





```

7.  What does the glimpse function do (we have not covered it)? How might you learn more about it?

```{r}



```
