---
title: "Intro - Problem Set KEY"
output: pdf_document
---

# Problem Set for Intro to R KEY

### Your Name (replace me)

### Date (replace me)

**DUE THURSDAY, Sept 8th AT MIDNIGHT**\
Download this file, and turn it in on Moodle.\
\
(to download a file, check the checkbox next to the file in the lower-right window, and click the gear, then Export....)

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

1.  In the code chunk below, define what a variable is (using comments), and create a variable `myVariable` set equal to 20.

```{r}

# A variable is a letter, word, or series of words that can store a value (number, word, vector, data set) in R


myVariable<-20


```

2.  Describe what a vector is in R, and create a sample vector below:

```{r}

# A vector is a type of variable that stores multiple values

myVector<-c(1,2,3,4,5)


```

3.  In the code chunk below, load the tidyverse. Why might we do this, and what is the tidyverse for?

```{r}

library(tidyverse)

# Loading the tidyverse provides additional functions for R programming.

# The tidyverse is a series of packages and functions written by data scientists to make working with data easier.


```

4.  Describe what a function is. What is an argument? How might you learn about what functions exist in R?

```{r}

# A function is a built in command that performs common tasks.

# An argument is a thing (variable, data set, etc.) that you provide to a function as input.

# You can learn about what functions exist by searching the internet.


```

5.  What is camel case? Describe some best practices for naming variables.

```{r}

# Camel case is a syntax for creating variable names in which the first word is lower case, and subsequent words are title case, with no spaces.

# Variables should be named in such a manner that they are readable (e.g. with camel case), and that they accurately describe what the variable contains.


```

6.  What is the mean for the survey responses for self reported willingness to settle in a remote environment (hint: use the `remote` column)

```{r}

teamAntarcticaData<-read_csv("teamAntarcticaData.csv")

remote<-teamAntarcticaData$remote

mean(remote)




```

7.  What does the glimpse function do (we have not covered it)? How might you learn more about it?

```{r}

# glimpse() lets you view your dataset in a transposed view (columns become rows)

# You can learn more about glimpse() by running help(glimpse). You can also find documentation/look for examples by searching the internet.

```
