---
title: "Analyzing Data with R - Problem Set"
output: pdf_document
---

# Problem Set for Analyzing Data with R

### Your Name (replace me)

### Date (replace me)

**DUE THURSDAY, Sept 15th AT MIDNIGHT**\
Download this file, and turn it in on Moodle.\
\
(to download a file, check the checkbox next to the file in the lower-right window, and click the gear, then Export....)

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

Run this code chunk first, to make the survey data available as the variable `classData`:

```{r}
classData<-read_csv("teamAntarcticaData.csv")
```

1.  Create a subset of `classData` of students who responded less than 3 on the fishing question, called `poorFishing`. How many reported less than 3?

```{r}

poorFishing<-classData %>% filter(fishing<3)

nrow(poorFishing)


```

2.  Describe logical operators, and how they can be used in the `filter` function:

```{r}

# Logical operators are a logical action or process, like "&" or "|". They allow you to have multiple conditions in the filter function.


```

3.  How many Lewis & Clark students voted to have the bear as the team flag? Show code below how you would derive your answer:

```{r}

lcBear<-classData %>% filter(school=="Lewis & Clark College" & teamFlag=="Bear")

nrow(lcBear)


```

4.  What is the "pipe" in R? What is it used for?

```{r}

# The pipe, %>%, is a tidyverse convention that allows you to chain data and functions together. 

```

5.  Determine the mean and standard deviation of self-reported bedside manner, comparing Lewis & Clark to University of Arizona students:

```{r}

bedsideMannerData<- classData %>% group_by(school) %>% 
  summarize(bedsideAvg=mean(bedsideManner), bedsideSd=sd(bedsideManner))

bedsideMannerData

```

6.  Create a data set showing the percentage of votes for team flag animal, *just* for Lewis & Clark students:

```{r}

lc<-classData %>% filter(school=="Lewis & Clark College")

lcTotal<-nrow(lc)

lcFlagPercentage<-lc %>% group_by(teamFlag) %>% summarize(percentage=n()/lcTotal)

lcFlagPercentage


```
