---
title: "R Notebook"
author: "Jeremy McWilliams"
output: html_notebook
---

# Introduction to R and Data Concepts
## September 7th, 2022


### Goals
* Gain some familiarity and comfort with rstudio
* Learn how to assign variables 
* Learn about and use functions 
* Write code to work with a data set


### What's the deal with this document?

This type of document is called an "R Notebook". It's basically a mix of text, code, and "R Markdown".
"R Markdown" is a shorthand for creating formatted text in documents. One of the neat things about R Notebooks is that you can "knit" it to an output like PDF or HTML. We'll see this in action at the end of this lesson.

Let's now look at "code chunks" by diving into R programming!


### Basic R 


The grey rectangle below is a "code chunk". Everything between the beginning and ending three backticks (```) is interpreted as R code. To run the code, click the green triangle in the upper-right corner.

In this example, R can perform basic math:

```{r}

2+2

```


Now it's your turn. Enter code below to subtract ten from twenty-two:

```{r}



```


#### Assigning Variables

