---
title: "Boxplots, bar plots, and error bars"
output: 
  html_document:
    css: "style.css"
---

```{r}
library(tidyverse)

library(palmerpenguins)

penguins<-palmerpenguins::penguins

penguins



```

### Box plots with error bars

Strategy: Use geom_boxplot(), and in the aes function, set x equal to a categorical column, which will automatically group them. For the horizontal lines (error bars), add stat_boxplot(geom = "errorbar").

```{r}


ggplot(data=penguins, mapping=aes(x=species, y=bill_length_mm, fill=species))+
  stat_boxplot(geom="errorbar")+
  geom_boxplot()+
  labs(title="Distribution of Penguin Bill lengths by Species",
       x="Species", y="Bill Length (mm)")





```

### Bar plots with error bars

Strategy: use group_by/summarize to calculate group mean and standard deviation. Add geom_errorbar, in which the top top bar is the mean + standard deviation, and the lower bar is the mean - standard deviation:

```{r}

groupedBillLength<- penguins %>% 
  group_by(species) %>%
  summarize(avgBillLength=mean(bill_length_mm, na.rm=TRUE), 
            sdBillLength=sd(bill_length_mm, na.rm=TRUE))

groupedBillLength

ggplot(data=groupedBillLength, mapping=aes(x=species, y=avgBillLength, fill=species))+
  geom_bar(stat="identity")+
  geom_errorbar(mapping=aes(ymin=avgBillLength-sdBillLength, 
                            ymax=avgBillLength+sdBillLength), width=0.2)+
  labs(title="Average Bill Length by Species", 
       x="Species", 
       y="Bill Length (mm)")






```

### Practice

Create a box plot comparing penguin mass among species. Include error bars, a legend, and labels.

```{r}
# create box plot below

ggplot(data=penguins, mapping=aes(x=species, y=body_mass_g, fill=species))+
  stat_boxplot(geom="errorbar")+
  geom_boxplot()+
  labs(title="Distribution of Penguin Mass by Species",
       x="Species", y="Mass (g)")
  

```

Create a bar plot comparing penguin mass among species. Include error bars (+/- 1 sd), a legend, and labels.

```{r}
# create bar plot below


groupedMass<- penguins %>% 
  group_by(species) %>%
  summarize(avgMass=mean(body_mass_g, na.rm=TRUE), 
            sdMass=sd(body_mass_g, na.rm=TRUE))

groupedMass

ggplot(data=groupedMass, mapping=aes(x=species, y=avgMass, fill=species))+
  geom_bar(stat="identity")+
  geom_errorbar(mapping=aes(ymin=avgMass-sdMass, 
                            ymax=avgMass+sdMass), width=0.2)+
  labs(title="Average Penguin Mass by Species", x="Species", y="Mass (g)")



```
