---
title: "Module 3: ANOVA"
author: "Mila Pruiett"
output:
  html_document: default
---

Your name:

Date:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Main Question: We want to know if the population of leopard seals differs between the bays.**

1.  To answer this question, which variable in the data set is the independent variable? Which is the dependent? (2pts)

```{r}
# independent is

# dependent is

```

2.  What are our null and alternative hypotheses? (2pts)

```{r}
# Null: 

# Alternative: 

```

3.  Load tidyverse and read in the data (2pts)

```{r}


```

4.  Create a histogram of the number of seals to see the distribution. Use facet_wrap(\~ bay) to create 6 histograms, one for each bay. (2pts)

```{r}

```

5.  Now let's calculate some summary statistics of the number of leopard seals per bay (mean and standard deviation). Which bay has the most leopard seals? Which has the least? (4pts)

```{r}

```

6.  Run an ANOVA to test if the mean number of seals varies between the bays. (4pts)

```{r}

```

7.  Interpret the ANOVA table you just created: What is the p-value? What is the F-statistic? Do you accept or reject the null hypothesis? What does that mean? (4pts)

```{r}


```
