---
title: 'Module 3: ANOVA'
author: "Mila Pruiett"
output:
  pdf_document: default
  html_document: default
---

Your name: Mila :)

Date:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Main Question: We want to know if the population of leopard seals differs between the bays.**

1. To answer this question, which variable in the data set is the independent variable? Which is the dependent? Which variable is categorical? Which variable is numeric? (4pts)

```{r}
# independent is the bay

# dependent is the number of seals

# categorical is bay

# numerical is number of seals

```

2.  What are our null and alternative hypotheses? (2pts)

```{r}
# Null: The mean number of leapord seals is the same at each of the bays

# Alternative: The mean number of leapord seals is not the same at all of the bays. At least one is different.  

```

3. Load tidyverse and read in the data, called "antarctic_seals_many_bays.csv" (2pts)

```{r}
library(tidyverse)
sealData <- read_csv("antarctic_seals_many_bays.csv")

```

4.  Create a histogram of the number of seals to see the distribution. Use facet_wrap(\~ bay) to create 6 histograms, one for each bay. (2pts)

```{r}
ggplot(sealData, aes(num_seals)) +
  geom_histogram() +
  facet_wrap(~bay)
```

5. Now let's calculate some summary statistics of the number of leopard seals per bay (mean and standard deviation). Which bay has the most leopard seals? Which has the least? (4pts)

```{r}
sealData %>% group_by(bay) %>% summarize(mean(num_seals), sd(num_seals))
# bay with lowest mean number of seals: Sulzberger
# bay with the greatest mean number of seals: Hope
```

6.  Run an ANOVA to test if the mean number of seals varies between the bays. (1pts)

```{r}
sealModel <- aov(data = sealData, num_seals ~ bay)
summary(sealModel)

```

7.  Interpret the ANOVA table you just created: What is the p-value? What is the F-statistic? What is our alpha level (cutoff value for p)? Do you accept or reject the null hypothesis? What does that mean? (5pts)

```{r}
# the p-value is smaller than 2 x 10 ^ - 16 
# the f-stat is 1129
# I reject the null hypothesis because the p-value of 2e-16 is smaller than my alpha of 0.05
# this means that at least one of the mean number of leopard seals is different in one of the bays


```
