---
title: 'Module 3: ANOVA'
author: "Mila Pruiett"
output:
  pdf_document: default
  html_document: default
---

Your name: Mila :)

Date:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Main Question: We want to know if the population of leopard seals differs between the bays.**

1. To answer this question, which variable in the data set is the independent variable? Which is the dependent? Which variable is categorical? Which variable is numeric? (4pts)

```{r}
# independent is the bay

# dependent is the number of seals

# categorical is bay

# numerical is number of seals

```

2.  What are our null and alternative hypotheses? (2pts)

```{r}
# Null: The mean number of leapord seals is the same at each of the bays

# Alternative: The mean number of leapord seals is not the same at all of the bays. At least one is different.  

```

3. Load tidyverse and read in the data, called "antarctic_seals_many_bays.csv" (2pts)

```{r}
library(tidyverse)
sealData <- read_csv("antarctic_seals_many_bays.csv")

```

4.  Create a histogram of the number of seals to see the distribution. Use facet_wrap(\~ bay) to create 6 histograms, one for each bay. (2pts)

```{r}
ggplot(sealData, aes(num_seals)) +
  geom_histogram() +
  facet_wrap(~bay)
```

5. Now let's calculate some summary statistics of the number of leopard seals per bay (mean and standard deviation). Which bay has the most leopard seals? Which has the least? (4pts)

```{r}
sealSummary <- sealData %>% group_by(bay) %>% summarize(meanSeals = mean(num_seals), sdSeals = sd(num_seals))
# bay with lowest mean number of seals: Sulzberger
# bay with the greatest mean number of seals: Hope

ggplot(data = sealSummary, aes(bay, meanSeals, fill = bay)) + 
  geom_bar(stat = "identity") +
    geom_errorbar( aes(ymin = meanSeals-sdSeals, ymax = meanSeals + sdSeals), 
              width = 0.2)  +
  xlab("Bay Name") +
  ylab("Mean Number of Seals") +
  ggtitle("Mean number of seals per bay")
```

6.  Run an ANOVA to test if the mean number of seals varies between the bays. (1pts)

```{r}
sealModel <- aov(data = sealData, num_seals ~ bay)
summary(sealModel)

```

7.  Interpret the ANOVA table you just created: What is the p-value? What is the F-statistic? What is our alpha level (cutoff value for p)? Do you accept or reject the null hypothesis? What does that mean? (5pts)

```{r}
# the p-value is smaller than 2 x 10 ^ - 16 
# the f-stat is 1129
# I reject the null hypothesis because the p-value of 2e-16 is smaller than my alpha of 0.05
# this means that at least one of the mean number of leopard seals is different in one of the bays


```


Mila making figure for class: tukeys results on graph
```{r}
generate_label_df <- function(TUKEY, variable){

  # Extract labels and factor levels from Tukey post-hoc 
  Tukey.levels <- TUKEY[[variable]][,4]
  Tukey.labels <- data.frame(multcompLetters(Tukey.levels)['Letters'])

  #I need to put the labels in the same order as in the boxplot :
  Tukey.labels$treatment=rownames(Tukey.labels)
  Tukey.labels=Tukey.labels[order(Tukey.labels$treatment) , ]
  return(Tukey.labels)
}

sealsManyBays2 <- sealsManyBays %>% select(num_seals, bay)

model=lm(sealsManyBays2$num_seals ~ sealsManyBays2$bay)
ANOVA=aov(model)

# Tukey test to study each pair of treatment :
TUKEY <- TukeyHSD(x=ANOVA, 'sealsManyBays2$bay', conf.level=0.95)

labels<-generate_label_df(TUKEY , "sealsManyBays2$bay")  #generate labels using function

names(labels)<-c('Letters','bay')#rename columns for merging

yvalue<-aggregate(.~ bay, data=sealsManyBays2, mean) # obtain letter position for y axis using means

final<-merge(labels, yvalue) #merge dataframes

ggplot(sealsManyBays2, aes(x = bay, y = num_seals, fill = bay)) +
  geom_blank() +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  labs(x = 'Bay', y = 'Number of Seals') +
  ggtitle("Differences in the number of seals by bay from Tukey's HSD")+
  theme(plot.title = element_text(hjust = 0.5, face='bold')) +
  geom_boxplot(stat = "boxplot") +
  geom_text(data = final, aes(x = bay, y = num_seals, label = Letters) ,vjust=-3.5,hjust=-.5) +
  theme(plot.title = element_text(vjust=-0.6))
```

