---
title: "Regression Homework"
author: "Mila Pruiett"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Statistical inference and regression analyses homework

### Your name:

### Date:

Score out of 20 points:

### The assignment

In this homework, you are going to look at the relationship between hairgrass density and another variable, the average summer temperature. The sites we sampled were along a gradient of summer temperatures, but we don't know if that is at all related to the growth of the hairgrass.

1.  First load the tidyverse and read in the data. (1 pts)

```{r}

```

2.  Calculate descriptive statistics for the temperature (mean and standard deviation). As a reminder, this should NOT be grouped by another categorical variable (our data set doesn't even have categorical variables) (2pts)

```{r}

```

3.  Create a scatter plot of hairgrass density and average summer temperature. Think carefully about which variable is the independent (x axis) and which is the dependent (y axis). Give your plot a title. hint: ggtitle("title here") Write a few sentences about what you think the relationship between hairgrass density and avg summer temperature is (is it related at all? are they positively related? negatively related?) (4 pts)

```{r}

```

4.  Calculate the correlation coefficient, r. Calculate r-squared. Interpret what r squared means for this relationship. (3pts)

```{r}

```

5.  What would the model for hairgrass density and summer temperature be? (Write it without the numbers for the coefficients) (1 pt)

```{r}

```

6.  What are the null and alternative hypothesis regarding the relationship between these two variables? (2 pts)

```{r}

```

7.  Create the model in R and obtain the summary of it. What is the model? What is the p-value associated with the F-statistic? Do we accept or reject the null hypothesis regarding the relationship between these two variables? What can we conclude then about building a road? (5 pts)

```{r}

```

8.  Create the scatter plot that includes the line of best fit (of which you now know the formula for)! (2 pts)

```{r}

```

REMEMBER TO SAVE THIS FILE BEFORE YOU EXPORT IT 