---
title: "Food Gone Bad / Data Viz - Problem Set"
output: pdf_document
---

# Problem Set for Food Gone Bad / Data Viz

### Your Name

### Date

**DUE THURSDAY, Sept 29th AT MIDNIGHT**

Instructions:

-   Replace Your Name and Date above with your name and the current date.

-   Complete the problem set below.

-   Download the file to your computer: Check the checkbox next to the file in the lower-right window, click the gear icon, and select Export.

-   Rename the file with this convention: Firstname-Lastname-week-5-problem-set.Rmd (e.g. Jane-Doe-problem-set-week3.Rmd

-   Upload this file to Moodle.\
    \

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

Run this code chunk first, to make the data set from the code along is available as the variable `sick`:

```{r}
library(tidyverse)
sick<-read_csv("sick_data.csv")
```

1.  What does "gg" in "ggplot" stand for? What are the three components of data visualizations?

```{r}

# GG stands for "Grammar of Graphics"

# The three components of data visualizations are:
# The Data
# The Aesthetics (the stuff you see)
# The Geom, or type of plot


```

2.   Create a histogram of the distribution of team member weights with ggplot. Make sure you add descriptive labels, and style the bars with colors.

```{r}

ggplot(data=sick, mapping=aes(x=weight_kg))+
  geom_histogram(bins=12, color="black", fill="grey" )+
  labs(title="Distribution of weight among Team Antarctica Members", y="Frequency", x="Weight (kg)")


```

3.  Create a scatter plot displaying participant weight with percent plant intake using ggplot. Label axes appropriately, and color the points.

```{r}

ggplot(data=sick, mapping=aes(x=weight_kg, y=perc_plant))+
  geom_point(color="blue")+
  labs(title="Association of team member weights with percent plant intake", x="Weight(kg)", y="Plants as percent of diet")


```

4.  Describe why you might use a histogram, scatter plot, or bar plot (i.e. what is the purpose of each?).

```{r}

# You would use a histogram to show frequency distribution for a single variable in a population.

# You would use a scatter plot to view associations (or lack thereof) between two numeric variables.

# You would use a bar plot to compare averages (or other statistical measures) among groups


```

5.  Generate a bar plot showing the average fish consumption among those who specialize in Management, Genetics, and Medicine. Include labels, and use the "fill" attribute to generate colors and a legend.

```{r}

fishConsumption<- sick %>% filter(specialties=="Management" | specialties=="Genetics" | specialties=="Medicine") %>%
  group_by(specialties) %>%
  summarize(avgFishConsumption=mean(perc_fish))


ggplot(data=fishConsumption, mapping=aes(x=specialties, y=avgFishConsumption, fill=specialties))+
  geom_bar(stat="identity")+
  labs(title="Average percent fish intake by Specialty", x="Specialty", y="Average percent fish intake")



```


6. For each of the three plots above, write code to save the files to "histogram.jpg", "scatterplot.jpg", and "barplot.jpg". (Hint: assign each plot to a variable as part of your answer)

```{r}

hgram<-ggplot(data=sick, mapping=aes(x=weight_kg))+
  geom_histogram(bins=12, color="black", fill="grey" )+
  labs(title="Distribution of weight among Team Antarctica Members", y="Frequency", x="Weight (kg)")

ggsave("histogram.jpg", hgram)
  
splot<-ggplot(data=sick, mapping=aes(x=weight_kg, y=perc_plant))+
  geom_point(color="blue")+
  labs(title="Association of team member weights with percent plant intake", x="Weight(kg)", y="Plants as percent of diet")

ggsave("scatterplot.jpg", splot)
  
barchart<-ggplot(data=fishConsumption, mapping=aes(x=specialties, y=avgFishConsumption, fill=specialties))+
  geom_bar(stat="identity")+
  labs(title="Average percent fish intake by Specialty", x="Specialty", y="Average percent fish intake")

ggsave("barplot.jpg", barchart)



```
