---
title: "Module 2: Food Gone Bad"
author: "Keaton Wilson, modified by EKB and Jeremy McWilliams"
output: pdf_document

editor_options: 
  markdown: 
    wrap: 72
  wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to Plotting

## Homework! This afternoon, the assignment "Week 5 Problem Set" will be available in the class workspace. Complete the week-5-problem-set.Rmd file, and submit it to Moodle by Thursday night at midnight (make sure you rename it using the firstname-lastname-...Rmd naming convention).

## Student Learning Outcomes

1.  Students will be able to apply basic data science knowledge to find
    the cause of a real-world scenario--food poisoning!
2.  Students will be able to use ggplot to generate histograms, scatter
    plots, and bar charts from data sets, and save them to image files.
3.  Students will be able to use visual-thinking skills to create
    visualizations that allow them to explore patterns in data, draw
    inferences, and create solutions.

## Introduction to the problem

We have a wave of people getting sick across the team. People are coming
in complaining of stomach sickness. Doctors have ruled out a
communicable viral infection like norovirus, so it seems likely to be a
food contamination issue.

The two main sources of food that are grown on site and distributed to
team members are [plants grown in hydroponic
greenhouses](https://thespoon.tech/scientists-in-antarctica-grow-food-without-soil-or-sunlight-get-ready-mars/)
(mostly Swiss chard, cucumbers and radishes) and fish (tilapia, a
tolerant warm-water species, and rainbow trout, a cold-water species).
Team members vary in the composition of their diet; people are allowed
to choose how much of different food sources they eat.

Fortunately, we have some data to work with! We have data on the
following:

-   which team members are sick
-   how much fish or plant material they incorporate into their diets

### Quick Discussion

How might we go about trying to figure out what is causing the problem?

## The Data

First we're going to pull in the data and give it a quick
inspection/exploration before we start to work through some of the
visualization tools in R.

```{r}
#load tidyverse


# assign data set to variable "sick"


```

## Histograms

We're going to look at a couple ways to create a histogram. The first is
with the base R function `hist`, and the second is with `ggplot` (from
the `tidyverse`). From today forward we're going to exclusively use
ggplot for data visualizations, as it's the standard in R/data science.

Let's first look at the `hist` function.

```{r}
# use base R "hist" function


```

Now let's create a histogram with the same data using ggplot. First,
let's talk a little about ggplot:

### What is ggplot?

ggplot is an R package, and is part of the tidyverse. The "gg"
translates to "grammar of graphics", and is founded in the idea that all
data visualizations are comprised of three components:

-   data set
-   aesthetics, or visual marks that represent the data (i.e. the stuff
    that you see)
-   geometric objects, or "geoms" (e.g the type of plot)

In the files tab (lower-right window), take a look at the
ggplot-cheatsheet.pdf. In addition, there's lots of documentation on the
internet on ggplot.

```{r}

# Data set: "data=sick"              (the data set)
# Aesthetics: "mapping=aes(x=age)"   (the stuff you see)
# Geoms: "geom_histogram()"          (what type of plot)

# Notice that the "+" is used to chain functions together in ggplot



# 'bins' refers to the number of ranges data can fall in
```

We can improve the look by adding the "color" and "fill" attributes to
geom_histogram. `color` indicates the outline color, and `fill`
specifies the background color:

```{r}
# add color and fill attributes to geom_histogram()



```

One of the keys to data visualization is making sure the data and units
are very clear to the viewer. We can chain on the labs() function to
create custom axis labels and title:

```{r}

# chain "labs()" to the plot code





```

Create a histogram showing the distribution of height from the sick data
set. Use the techniques show above to style it, and provide custom
labels:

```{r}




```

## Scatter plots

Scatter plots are useful for visualizing if there is a potential
association between two variables. Let's take a look at an example
scatter plot, displaying age on the x-axis (independent variable), and
weight on the y-axis (dependent variable). You'll see this is pretty
similar to histogram code above, except for an additional attribute in
the mapping aes function (y=), and a different geom function
(geom_point):

```{r}

# use ggplot with geom_point()




```

Try improving this plot by adding a title, x- and y-axis labels, and
perhaps some color.

```{r}

#add color attribute to geom_point, and chain labs() at the end


```

In your group or with your neighbor, create a scatter plot to show what
variables might be associated to give some clues about the root of the
sickness. Use proper labels and add some color. Try some different
variables until you see what might be a pattern.

```{r}

# What two variables might be useful in solving the mystery? Try multiple combinations if needed.


```

## Bar Plots

Lastly we're going to look at bar plots. One key difference between bar
plots and the previous two plots we examined is that bar plots often
show summary statistics of categorical variables, instead of all data.
As such, we'll need to use strategies from Module 1 to group data and
generate statistics.

Let's say we're interested in creating a visualization showing the means
on doctor visits in males and females. First we'll need to group the
data and generate the means, using group_by/summarize:

```{r}



```

Now that we have our data grouped with the average doctor visits, let's
use it to create a bar chart:

```{r}

# use ggplot with geom_bar function. stat="identity" means use the data values from the data set for the y-axis, rather than count




```

## 

We can improve this in a couple ways. Like before we can add better
labeling with labs. But we can also add some color and a legend by using
the "fill" attribute in the aes function, and set it to the sex
variable:

```{r}

#add labs()


```

Let's say were interested in comparing average plant consumption among
team members who specialize in Climatology, Data Science, and
Psychology. Create a bar plot below showing the average plant
consumption among the three groups (hint: you may need to filter your
data first).

```{r}

# create your subset of data from 'sick' first, then group_by/summarize



# now use this subset for generating the bar plot



```

## Saving plots

It's likely at some point you may want to save your plots to image
files. There's a handy function to do this: `ggsave`. ggsave takes the
argument of an image file name (e.g. myPlot.jpg), and optionally a
variable, if you have your plot assigned to a variable - if not, it will
save the last plot rendered.

```{r}

# create a plot, but assign it to a variable



# use ggsave to save it to a file


```

## Homework Reminder! This afternoon, the assignment "Week 5 Problem Set" will be available in the class workspace. Complete the week-5-problem-set.Rmd file, and submit it to Moodle by Thursday night at midnight (make sure you rename it using the firstname-lastname-...Rmd naming convention).
