---
title: "Regression Code Along"
author: "Mila Pruiett"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regression Analyses Continued

We are going to continue figuring out what environmental parameters are important for the hairgrass (the really awesome vascular plant in the arctic). Last week, we found that hairgrass density was significantly positively correlated with nitrogen content and the average summer temperature.

Each small group will look at a different variable. The remaining variables are

-   phosphorous content

-   percentage of soil that is rock

-   monthly maximum wind speed in knots

-   average UV index

-   average winter temperature (C)

-   penguin density (per 5 sq m within 100 m of the hairgrass quadrants)

**Write your group's variable here:**

As you go, please populate the appropriate slide deck

11:30 Class <https://docs.google.com/presentation/d/1X9qGtxDMBo4eRk2SY_ogTLZjY6NoxAhbtb4SE3QZKag/edit#slide=id.p>

1:50 Class <https://docs.google.com/presentation/d/1EZ9Z1XhR_NMnc1xMuEtOlUuuYi-8gPr52a4bdM8D8IE/edit#slide=id.p>

Load the tidyverse and read in your data

```{r}

```

1.  Create a scatter plot with the line of best fit for hairgrass density and your variable. Be sure to add a title and label the axes with units.

```{r}

```

2.  Create a linear regression with hairgrass density and your variable.

```{r}

```

3.  What is the formula for the line of best fit?

```{r}

```

4.  Is your variable significant in predicting hairgrass density? (Is the p-value associated with the F-stat significant at alpha = 0.05?)

```{r}

```
