---
title: "t-test-hw-Key"
author: "Mila Pruiett"
date: "2022-11-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. (2 points) Describe null and alternative hypotheses for:

-   The difference in means of seal count in Wilhelmenia vs. Marguarite bay
-   the difference in means of fish count in Wilhelmenia vs. Marguarite bay

Q2. (2 points) Generate helpful visualizations and descriptive statistics for the above data

Q3. (4 points) Perform t-tests to evaluate your hypotheses, and interpret the results. Reject the null hypothesis if p\<0.05.

### Answers

Q1.

$H_{0}$: There is no difference in the mean seal count in Wilhelmia and Marguarite bay.
        There is no difference in the mean fish count in Wilhelmia and Marguarite bay.


$H_{a}$:There is a difference in the mean seal count in Wilhelmia and Marguarite bay.
        There is a difference in the mean fish count in Wilhelmia and Marguarite bay.

Q2.

```{r}
library("tidyverse")
seals <- read_csv("arctic-seals.csv")
fish <- read_csv("arctic-fish.csv")

# descriptive stats
summarySeals <- seals %>% group_by(bay) %>% summarize(mean(num_seals), sd(num_seals))
summaryFish <- fish %>% group_by(bay) %>% summarize(mean(num_fish), sd(num_fish))

# data visualization: best to do a boxplot or bar chart
sealsPlot <- seals %>% 
  ggplot(aes(bay, num_seals, fill= bay)) +
  geom_boxplot() +
  xlab("Bay Identity") +
  ylab("Number of Seals")

fishPlot <- fish %>% ggplot(aes(bay, num_fish, fill = bay)) +
  geom_boxplot() +
  xlab("Bay Identity") +
  ylab("Number of Fish")


summarySeals
summaryFish
sealsPlot
fishPlot

```

Q3.

```{r}
# t test for seals
sealsT <- t.test(data = seals, num_seals ~ bay)
sealsT
# Interpretation: The p-value is 0.0000272, which is less than our alpha level of 0.05, so we can reject the null. 
# We conclude that the mean number of seals is different between Marguarite and Wilhelmia Bay

# t test for fish
fishT <- t.test(data = fish, num_fish ~ bay)
fishT
# Interpretation: The p-value was 0.08, which is greater than our alpha level of 0.05, so we cannot reject the null.
# We conclude that the mean number of fish is not different between Marguarite and Wilhelmia Bay.

```
